---
title: "Simulating a Smaller TAM Panel"
subtitle: "10 samples of 1,000 individuals, weighted to the universe and matched against TAM spot results"
date: today
output-file: index
format:
  revealjs:
    slide-number: true
    smaller: true
    scrollable: true
    embed-resources: true
    logo: assets/3m3a-logo.png
    theme: [default, 3m3a-theme.scss]
title-slide-attributes:
  data-background-color: "#0E2841"
execute:
  echo: false
  message: false
  warning: false
---

```{r}
#| label: setup
#| include: false

library(tidyverse)
library(readxl)
library(janitor)
library(anesrake)
library(data.table)
library(gt)
library(ggdist)

universe_size <- 17128055
```

```{r}
#| label: load-data
#| include: false

demfile  <- read_rds("demIndMay25_May31.rds")
swdfile  <- read_rds("viewingMay25_May31.rds")
hhfile   <- read_rds("HHsMay25_May31.rds")
demo_nat <- read_excel("KSA-TX4 Definition 20250626_External.xlsx", sheet = "TX4-Demo-National")

# Spots from the full TAM panel. Excel stores pure times on 1899-12-31,
# so re-attach the real date from the Date column.
spots <- read_excel("RobertTables.xlsx", sheet = "Spots") |>
  mutate(
    `Start Time` = as.POSIXct(paste(as.Date(Date), format(`Start Time`, "%H:%M:%S"))),
    `End Time`   = as.POSIXct(paste(as.Date(Date), format(`End Time`,   "%H:%M:%S")))
  )

demfile <- demfile |> filter(member_id != "zz")
```

```{r}
#| label: parse-demographics
#| include: false

# Decode the INDdemos / HHdemos position strings into labelled columns,
# using the TX4 definition file.

# Individuals
ind_def <- demo_nat |>
  filter(`Level (HH/Ind)` == "INDIVIDUALS", !is.na(`Position in TX4`), !is.na(Value)) |>
  transmute(
    pos       = as.integer(`Position in TX4`),
    value_chr = trimws(Value),
    var_name  = Variable,
    label     = `Reporting-eTAM`
  )

var_name_map <- ind_def |>
  distinct(pos, var_name) |>
  mutate(col_name = make.names(var_name) |>
           str_replace_all("\\.+", "_") |>
           str_remove("_$"))

ind_def <- ind_def |> left_join(var_name_map, by = c("pos", "var_name"))

setDT(demfile)

for (p in sort(unique(ind_def$pos))) {
  col     <- var_name_map$col_name[var_name_map$pos == p]
  raw_col <- paste0("_raw_pos", p)
  demfile[, (raw_col) := substr(INDdemos, p, p)]

  lkp <- ind_def |>
    filter(pos == p) |>
    select(value_chr, label) |>
    mutate(value_chr = str_remove(value_chr, "\\.0$"))

  lkp_vec <- setNames(lkp$label, lkp$value_chr)
  demfile[, (col) := lkp_vec[get(raw_col)]]
  demfile[, (raw_col) := NULL]
}

# Households
hh_def <- demo_nat |>
  filter(`Level (HH/Ind)` == "HOUSEHOLD", !is.na(`Position in TX4`), !is.na(`Reporting-eTAM`)) |>
  transmute(
    pos       = as.integer(`Position in TX4`),
    value_chr = trimws(Value),
    var_name  = Variable,
    label     = `Reporting-eTAM`
  )

hh_var_map <- hh_def |>
  distinct(pos, var_name) |>
  mutate(col_name = make.names(var_name) |>
           str_replace_all("\\.+", "_") |>
           str_remove("_$"))

hh_def <- hh_def |> left_join(hh_var_map, by = c("pos", "var_name"))

setDT(hhfile)

for (p in sort(unique(hh_def$pos))) {
  col     <- hh_var_map$col_name[hh_var_map$pos == p]
  raw_col <- paste0("_raw_pos", p)
  hhfile[, (raw_col) := substr(HHdemos, p, p)]

  lkp_vec <- hh_def |>
    filter(pos == p) |>
    mutate(value_chr = str_remove(value_chr, "\\.0$")) |>
    { \(d) setNames(d$label, d$value_chr) }()

  hhfile[, (col) := lkp_vec[get(raw_col)]]
  hhfile[, (raw_col) := NULL]
}

# Bring household-level variables onto the individual file
hh_cols_to_add <- c("HHwgt", "Household_Size", "Dwelling_Type")
demfile <- hhfile[, c("file", "HHid", hh_cols_to_add), with = FALSE][
  demfile, on = c("file", "HHid")
]
```

```{r}
#| label: tv-counts
#| include: false

# Count TVs per household directly from the raw TX4 files (rim 4 input)
tx4_files <- list.files("tx4", pattern = "\\.tx4$", full.names = TRUE)

tv_list <- lapply(tx4_files, function(path) {
  fname  <- basename(path)
  lines  <- readLines(path, warn = FALSE)
  hh_idx <- which(substr(lines, 1, 1) == "H")

  tv_counts <- integer(length(hh_idx))
  hhids     <- character(length(hh_idx))

  for (i in seq_along(hh_idx)) {
    hhids[i] <- sub("^H([^_]+)_.*", "\\1", lines[hh_idx[i]])
    start    <- hh_idx[i] + 1
    end      <- if (i < length(hh_idx)) hh_idx[i + 1] - 1 else length(lines)
    block    <- lines[start:end]
    tv_counts[i] <- sum(substr(block, 1, 1) == "T")
  }

  data.table(file = fname, HHid = hhids, `TVs in HH` = tv_counts)
})

tv_dt   <- rbindlist(tv_list)
demfile <- tv_dt[demfile, on = c("file", "HHid")]
```

```{r}
#| label: build-rims
#| include: false

# Five raking dimensions (rim variables). Age is deliberately excluded
# so that all ages — including children — can be sampled and weighted.

demfile$rim1 <- factor(demfile$Nationality,
  levels = c("Nationality - Saudi", "Nationality - Arab Expats", "Nationality - Non-Arab Expats"),
  labels = c("Saudi", "Arab Expats", "Non-Arab Expats"))

demfile$rim2 <- factor(demfile$Region_Cluster,
  levels = c(
    "Detailed Region Split - Central Region",
    "Detailed Region Split - Western Region",
    "Detailed Region Split - Eastern Region",
    "Detailed Region Split - Northen Region",
    "Detailed Region Split - Southern Region"
  ),
  labels = c(
    "Central Region Cities",
    "Western Region Cities",
    "Eastern Region Cities",
    "North + South Region Cities",
    "North + South Region Cities"
  ))

demfile[, rim3 := fcase(
  Nationality == "Nationality - Saudi" & Household_Size == "Household Size - 1-2", "Saudi 1-2",
  Nationality == "Nationality - Saudi" & Household_Size == "Household Size - 3-4", "Saudi 3-4",
  Nationality == "Nationality - Saudi" & Household_Size == "Household Size - 5-6", "Saudi 5-6",
  Nationality == "Nationality - Saudi" & Household_Size == "Household Size - 7+",  "Saudi 7+",
  Nationality != "Nationality - Saudi" & Household_Size == "Household Size - 1-2", "Non-Saudi 1-2",
  Nationality != "Nationality - Saudi" & Household_Size == "Household Size - 3-4", "Non-Saudi 3-4",
  Nationality != "Nationality - Saudi" & Household_Size %in% c("Household Size - 5-6", "Household Size - 7+"), "Non-Saudi 5+"
)]
demfile[, rim3 := factor(rim3, levels = c(
  "Saudi 1-2", "Saudi 3-4", "Saudi 5-6", "Saudi 7+",
  "Non-Saudi 1-2", "Non-Saudi 3-4", "Non-Saudi 5+"
))]

demfile$rim4 <- factor(
  if_else(demfile$`TVs in HH` == 1, "Single", "Multi"),
  levels = c("Single", "Multi"))

demfile[, rim5 := fcase(
  Nationality == "Nationality - Saudi" & Gender == "Male",   "Saudi Male",
  Nationality == "Nationality - Saudi" & Gender == "Female", "Saudi Female",
  Nationality != "Nationality - Saudi" & Gender == "Male",   "Non-Saudi Male",
  Nationality != "Nationality - Saudi" & Gender == "Female", "Non-Saudi Female"
)]
demfile[, rim5 := factor(rim5, levels = c(
  "Saudi Male", "Saudi Female", "Non-Saudi Male", "Non-Saudi Female"
))]
```

```{r}
#| label: rim-targets
#| include: false

# Population targets for the five rims (from the TAM establishment survey)
rim_targets <- list(
  rim1 = setNames(c(0.678, 0.278, 0.044),        levels(demfile$rim1)),
  rim2 = setNames(c(0.301, 0.388, 0.135, 0.176), levels(demfile$rim2)),
  rim3 = setNames(c(0.025, 0.134, 0.251, 0.268,
                    0.028, 0.098, 0.152),         levels(demfile$rim3)),
  rim4 = setNames(c(0.497, 0.503),                levels(demfile$rim4)),
  rim5 = setNames(c(0.343, 0.335, 0.183, 0.095), levels(demfile$rim5))
)
```

```{r}
#| label: draw-samples
#| include: false

# ── Sampling and daily raking ─────────────────────────────────────────────────
# 1. Draw 10 independent samples of 1,000 individuals (all ages) from the
#    panel as it stood on 20260525.
# 2. For every day of the week, rake the members present that day to the
#    rim targets — so each person gets a fresh weight every day, reflecting
#    that day's sample composition.
# 3. Scale each day's weights so they sum to the universe (17,128,055).

week_dates <- as.character(seq(as.Date("2026-05-25"), as.Date("2026-05-31"), by = "day") |>
                             format("%Y%m%d"))

demfile_week <- demfile[file_date %in% week_dates]
swdfile_week <- swdfile[Date      %in% week_dates]

dem_allages_ref <- demfile[file_date == "20260525"]

set.seed(42)
samples_v2 <- lapply(seq_len(10), function(i) {

  panel    <- as.data.frame(dplyr::slice_sample(dem_allages_ref, n = 1000))
  panel_dt <- data.table(HHid = panel$HHid, member_id = panel$member_id)

  daily <- lapply(week_dates, function(d) {
    day_df <- as.data.frame(
      demfile[file_date == d][panel_dt, on = .(HHid, member_id), nomatch = NULL]
    )
    if (nrow(day_df) < 50) return(NULL)

    day_df$caseid <- seq_len(nrow(day_df))

    rake <- tryCatch(
      anesrake(rim_targets, day_df,
               caseid  = day_df$caseid, pctlim = 2,
               verbose = FALSE, maxit  = 1000),
      error = function(e) NULL
    )
    if (is.null(rake)) return(NULL)

    data.table(
      HHid        = day_df$HHid,
      member_id   = day_df$member_id,
      file_date   = d,
      weight      = rake$weightvec,
      weight_proj = rake$weightvec / sum(rake$weightvec) * universe_size
    )
  })

  rbindlist(Filter(Negate(is.null), daily))
})

# Viewing data for each sample's panel members (whole week)
swdfile_samples <- lapply(seq_along(samples_v2), function(i) {
  panel_ids <- unique(samples_v2[[i]][, .(HHid, member_id)])
  swdfile_week[
    data.table(HHid = panel_ids$HHid, MemberCode = panel_ids$member_id),
    on = .(HHid, MemberCode), nomatch = NULL
  ]
})
```

```{r}
#| label: grp-computation
#| include: false

# ── Matching spots to the samples ────────────────────────────────────────────
# GRPAbsolute for a spot = sum of projected weights of everyone watching
# the spot's channel in the minute the spot starts.

# Broadcast minute helper (broadcast day starts 03:00)
to_bcast_min <- function(t) {
  h <- as.integer(substr(t, 1, 2))
  m <- as.integer(substr(t, 3, 4))
  (h * 60 + m) - (3 * 60)
}

spots_dt <- as.data.table(spots)[!is.na(Channel)]
spots_dt[, spot_id  := .I]
spots_dt[, date_chr := format(as.Date(Date), "%Y%m%d")]
spots_dt[, spot_min := to_bcast_min(format(`Start Time`, "%H%M%S"))]
# The spots file dates overnight spots (00:00-02:59) by broadcast day, so keep
# the date and wrap the minute past midnight instead of letting it go negative
spots_dt[spot_min < 0, spot_min := spot_min + 1440]

calc_grp <- function(swd_w, weight_col) {
  setDT(swd_w)
  if (!"start_min" %in% names(swd_w)) swd_w[, start_min := to_bcast_min(StartTime)]
  if (!"end_min"   %in% names(swd_w)) swd_w[, end_min   := to_bcast_min(EndTime)]
  swd_w[, .w := get(weight_col)]

  hits <- swd_w[spots_dt,
    on = .(ChannelName == Channel,
           Date        == date_chr,
           start_min   <= spot_min,
           end_min     >= spot_min),
    .(spot_id = i.spot_id, w = .w),
    nomatch = NULL
  ]
  hits[, .(grp = sum(w, na.rm = TRUE)), by = spot_id]
}

# Full TAM reference, recalculated: official INDWgt per person per day
ind_wgt_week <- demfile_week[, .(HHid, member_id, file_date, INDWgt)]
swd_tam <- merge(swdfile_week, ind_wgt_week,
                 by.x = c("HHid", "MemberCode", "Date"),
                 by.y = c("HHid", "member_id", "file_date"),
                 all.x = FALSE)
grp_tam <- calc_grp(swd_tam, "INDWgt")

# The 10 samples: daily projected weights joined by person AND date
grp_list <- lapply(seq_along(samples_v2), function(i) {
  swd_i <- copy(as.data.table(swdfile_samples[[i]]))
  wgt_i <- samples_v2[[i]][, .(HHid, member_id, file_date, weight_proj)]
  swd_i <- merge(swd_i, wgt_i,
                 by.x = c("HHid", "MemberCode", "Date"),
                 by.y = c("HHid", "member_id",  "file_date"),
                 all.x = FALSE)
  res <- calc_grp(swd_i, "weight_proj")
  setnames(res, "grp", paste0("S", i))
  res
})

# ── Assemble the comparison table ─────────────────────────────────────────────
base <- spots_dt[, .(
  spot_id, Product, Channel,
  Date    = as.Date(Date),
  Start   = format(`Start Time`, "%H:%M:%S"),
  GRP_TAM = GRPAbsolute
)]

base <- merge(base, grp_tam, by = "spot_id", all.x = TRUE)
setnames(base, "grp", "GRP_TAM_calc")

samp_cols <- paste0("S", 1:10)
for (i in seq_along(grp_list)) {
  s <- grp_list[[i]]
  if (!is.null(s) && nrow(s) > 0)
    base <- merge(base, s, by = "spot_id", all.x = TRUE)
}
for (col in samp_cols)
  if (!col %in% names(base)) base[, (col) := 0L]
for (col in c("GRP_TAM_calc", samp_cols))
  set(base, which(is.na(base[[col]])), col, 0L)

base[, spot_id := NULL]

base_df        <- as.data.frame(base)
samp_mat       <- as.matrix(base_df[, samp_cols])
base_df$S_mean <- rowMeans(samp_mat)
row_sd         <- apply(samp_mat, 1, sd)
base_df$S_cv   <- ifelse(base_df$S_mean > 0, row_sd / base_df$S_mean * 100, NA_real_)
```

## The question

Can a panel of **1,000 individuals** reproduce the results of the full TAM panel?

To find out, we:

1.  Draw **10 independent samples** of 1,000 individuals from the TAM panel
2.  **Weight each sample daily** to the population structure of Saudi Arabia, projecting to the TV universe of **17,128,055 individuals**
3.  Take a real list of **advertising spots** measured by the full TAM panel and recompute each spot's audience (GRP) from each of the 10 small samples
4.  Compare the small-sample GRPs against the TAM benchmark

## Process overview

```{mermaid}
flowchart LR
  A["TAM panel<br/>week 25–31 May 2026"] --> B["Draw 10 samples<br/>of 1,000 individuals<br/>(all ages)"]
  B --> C["Rake each sample<br/>day by day<br/>(5 rim dimensions)"]
  C --> D["Project weights<br/>to universe<br/>17,128,055"]
  E["Spot list<br/>(full TAM GRPs)"] --> F["Match each spot:<br/>channel + date +<br/>start minute"]
  D --> F
  F --> G["Compare GRP:<br/>TAM vs S1–S10"]
```

## Weighting targets

Each daily subsample is raked to five population dimensions. Age is excluded so that **all ages — including children — can be sampled**, matching the universe behind the spot GRPs.

```{r}
#| label: rim-targets-prep

rim_labels <- c(
  "Rim 1: Nationality",
  "Rim 2: Region",
  "Rim 3: HH Size x Nationality",
  "Rim 4: TVs in HH",
  "Rim 5: Gender x Nationality"
)

rims_df <- do.call(rbind, lapply(seq_along(rim_targets), function(i) {
  data.frame(
    rim      = rim_labels[i],
    category = names(rim_targets[[i]]),
    prop     = unname(rim_targets[[i]])
  )
}))

rims_gt <- function(df) {
  df |>
    gt(groupname_col = "rim") |>
    cols_label(category = "Category", prop = "Target %") |>
    fmt_percent(columns = prop, decimals = 1) |>
    tab_style(style = cell_text(weight = "bold"),
              locations = cells_row_groups()) |>
    tab_options(table.font.size = 16, data_row.padding = px(2))
}
```

::::: columns
::: {.column width="48%"}
```{r}
#| label: rim-targets-left
rims_gt(rims_df[rims_df$rim %in% rim_labels[1:2], ])
```
:::

::: {.column width="48%"}
```{r}
#| label: rim-targets-right
rims_gt(rims_df[rims_df$rim %in% rim_labels[3:5], ])
```
:::
:::::

## Drawing the samples

- Sampling frame: **all individuals present in the panel on 25 May 2026**
- Each of the 10 draws selects 1,000 individuals at random
- For **every day of the week**, the members present that day are raked independently — so each person receives a **new weight every day**, reflecting that day's sample composition
- Daily weights are scaled so each day sums to the universe of 17,128,055

```{r}
#| label: tbl-sanity

data.frame(
  Sample          = seq_along(samples_v2),
  `Panel members` = sapply(samples_v2, \(x) uniqueN(paste(x$HHid, x$member_id))),
  `Dates raked`   = sapply(samples_v2, \(x) uniqueN(x$file_date)),
  check.names = FALSE
) |>
  gt() |>
  tab_options(table.font.size = 18, data_row.padding = px(2))
```

## Weight distributions

With only 1,000 people representing 17.1 million, the average projected weight is roughly 17,000 — each panelist "stands in" for about 17,000 individuals. The full TAM panel carries much smaller weights (mean ≈ 2,000) because it has far more members spread across the same universe, so each person represents fewer individuals.

```{r}
#| label: tbl-weights

summarise_weights <- function(w, label) {
  data.frame(
    Sample = label,
    N      = length(w),
    Min    = round(min(w)),
    Median = round(median(w)),
    Mean   = round(mean(w)),
    Max    = round(max(w)),
    SD     = round(sd(w))
  )
}

# Full TAM panel: official INDWgt averaged per individual across days
tam_per_ind <- ind_wgt_week[, .(INDWgt = mean(INDWgt)), by = .(HHid, member_id)]
tam_summary <- summarise_weights(tam_per_ind$INDWgt, "TAM")

sample_summary <- lapply(seq_along(samples_v2), function(i) {
  per_ind <- samples_v2[[i]][, .(weight_proj = mean(weight_proj)), by = .(HHid, member_id)]
  summarise_weights(per_ind$weight_proj, as.character(i))
}) |> do.call(rbind, args = _)

weight_summary <- rbind(tam_summary, sample_summary)

weight_summary |>
  gt() |>
  fmt_number(columns = c(N, Min, Median, Mean, Max, SD), decimals = 0, use_seps = TRUE) |>
  cols_label(N = "Members") |>
  tab_header(title = "Projected weight per individual (averaged across days)") |>
  tab_style(
    style     = cell_fill(color = "#ECF0F4"),
    locations = cells_body(rows = Sample == "TAM")
  ) |>
  tab_options(table.font.size = 18, data_row.padding = px(2))
```

## Weight distributions, visualised

```{r}
#| label: weights-violin
#| fig-width: 12
#| fig-height: 6.5

weights_long <- rbind(
  data.table(group = "TAM", weight = tam_per_ind$INDWgt),
  rbindlist(lapply(seq_along(samples_v2), function(i) {
    per_ind <- samples_v2[[i]][, .(w = mean(weight_proj)), by = .(HHid, member_id)]
    data.table(group = paste0("S", i), weight = per_ind$w)
  }))
)
weights_long[, group := factor(group, levels = c("TAM", paste0("S", 1:10)))]

ggplot(weights_long, aes(x = weight, y = fct_rev(group), fill = group == "TAM")) +
  geom_violin(colour = NA, alpha = 0.9, scale = "width") +
  geom_boxplot(width = 0.12, outlier.size = 0.4, fill = "white", alpha = 0.8) +
  scale_x_log10(labels = scales::comma) +
  scale_fill_manual(values = c("TRUE" = "#E97132", "FALSE" = "#50C2C0"), guide = "none") +
  labs(
    x = "Projected weight per individual (log scale)",
    y = NULL,
    title = "Full TAM panel vs. 10 simulated samples"
  ) +
  theme_minimal(base_size = 14)
```

The full TAM panel (orange) sits far to the left at much smaller weights, while the 10 samples (teal) cluster tightly around ≈ 17,000 with similar, well-behaved spreads.

## Weight distributions, raincloud

```{r}
#| label: weights-raincloud
#| fig-width: 12
#| fig-height: 6.5

set.seed(6271)
# Subsample raw points for the "rain" so the dotplots stay legible
weights_dots <- weights_long[, .SD[sample(.N, min(.N, 300))], by = group]

ggplot(weights_long, aes(x = weight, y = fct_rev(group), fill = group == "TAM")) +
  stat_halfeye(adjust = 0.6, width = 0.7, justification = -0.15,
               .width = 0, point_colour = NA, colour = NA, alpha = 0.9) +
  geom_boxplot(width = 0.12, outlier.shape = NA, alpha = 0.5) +
  stat_dots(data = weights_dots, side = "bottom", justification = 1.05,
            dotsize = 0.5, colour = NA) +
  scale_x_log10(labels = scales::comma) +
  scale_fill_manual(values = c("TRUE" = "#E97132", "FALSE" = "#50C2C0"), guide = "none") +
  labs(
    x = "Projected weight per individual (log scale)",
    y = NULL,
    title = "Half-violin + raw points (300 sampled per group)"
  ) +
  theme_minimal(base_size = 14)
```

The raincloud adds the raw points (a 300-member sample per group) beneath each half-violin, making the actual data density visible alongside the smoothed shape and the box.

## Matching the spot list

The spot list comes from the **full TAM panel** and covers the same week.

For every spot we compute:

> **GRPAbsolute** = sum of projected weights of all sample members watching the spot's **channel** in the **minute the spot starts**, on the spot's **date** — using that day's weights.

The same calculation, applied to the full TAM panel with its official weights (`INDWgt`), reproduces the benchmark and validates the method.

```{r}
#| label: spot-match-stats

# Keep spots where the recalculated GRP matches the spots file (as displayed, whole numbers)
keep <- round(base_df$GRP_TAM) == round(base_df$GRP_TAM_calc)

n_spots   <- sum(keep)
n_matched <- sum(base_df$S_mean[keep] > 0)
```

Of the **`r nrow(base_df)` spots** in the list, **`r n_spots`** have a recalculated GRP matching the spots file and are kept for the comparison. The 10 samples found viewers for **`r n_matched`** of these — the remainder aired in minutes where no sampled panelist was watching that channel.

## GRP: full TAM vs. 10 samples {.scrollable}

```{r}
#| label: tbl-grp

base_df |>
  # Keep only spots where the recalculated GRP matches the spots file (as displayed, whole numbers)
  filter(round(GRP_TAM) == round(GRP_TAM_calc)) |>
  gt() |>
  tab_header(
    title    = "GRPAbsolute per spot",
    subtitle = "TAM benchmark vs. 10 simulated samples of 1,000 (S1–S10); only spots where the recalculation matches the spots file"
  ) |>
  tab_spanner(label = "Reference",         columns = c(GRP_TAM, GRP_TAM_calc)) |>
  tab_spanner(label = "Simulated samples", columns = all_of(samp_cols)) |>
  tab_spanner(label = "Sample summary",    columns = c("S_mean", "S_cv")) |>
  fmt_number(columns = c(GRP_TAM, GRP_TAM_calc, all_of(samp_cols), S_mean),
             decimals = 0, use_seps = TRUE) |>
  fmt_number(columns = "S_cv", decimals = 1, suffix = "%") |>
  fmt_missing(columns = "S_cv", missing_text = "—") |>
  cols_label(
    GRP_TAM      = "Spots file",
    GRP_TAM_calc = "Recalculated",
    S_mean       = "Mean",
    S_cv         = "CV"
  ) |>
  tab_style(
    style     = cell_fill(color = "#fff3cd"),
    locations = cells_body(
      columns = "S_cv",
      rows    = !is.na(S_cv) & S_cv > 100
    )
  ) |>
  tab_options(table.font.size = 13, data_row.padding = px(2))
```

**CV (coefficient of variation)** is the spread of the 10 sample GRPs relative to their average (standard deviation ÷ mean, as a percent): low means the samples agree and the estimate is stable, while rows above 100% — highlighted in yellow — scatter more than their own average.

## Total campaign GRP

```{r}
#| label: tbl-totals

totals <- data.frame(
  Source = c("TAM (spots file)", "TAM (recalculated)", paste("Sample", 1:10), "Sample mean"),
  GRP    = c(sum(base_df$GRP_TAM[keep]), sum(base_df$GRP_TAM_calc[keep]),
             colSums(samp_mat[keep, ]), mean(colSums(samp_mat[keep, ])))
)

totals |>
  gt() |>
  fmt_number(columns = GRP, decimals = 0, use_seps = TRUE) |>
  tab_options(table.font.size = 18, data_row.padding = px(2))
```

## Takeaways

- A 1,000-person sample carries **high projected weights** (\~17,000 per person), so single-spot GRPs are driven by very few viewers
- Spot-level estimates are therefore **volatile** — the CV column flags spots where the 10 samples disagree strongly
- Aggregated (campaign-level) GRPs are far more stable than individual spot GRPs
- Overnight spots carry high GRPs that the small samples capture less well — including them moves the sample mean from slightly above to **\~6% below** the TAM benchmark